---
title: "ppcm: Predictive Partly Conditional Model"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

The $\mathtt{ppcm}$ package aims to provide user-friendly functions to implement 
a predictive partly conditional model to characterize disease progression at
time $t$ with longitudinal ordinal outcomes in the presence of time-dependent
covariates at time $s$ ($s < t$) and time-dependent effects.

## Installation

You can install the $\mathtt{ppcm}$ package from GitHub with:

```{r install, eval = FALSE}
# install.packages("devtools")
devtools::install_github("liud4/ppcm")
```

## Import Dataset

```{r import_data, warning = FALSE, message = FALSE}
example.df <- readr::read_csv(system.file("extdata", "example_data.csv", package = "ppcm"))
head(example.df)
```

## Implementation

```{r implementation}
ppcm.fit <- ppcm::ppcm(
  data = example.df,
  id.var = "id",
  outcome.var = "outcome",
  time.var = "time",
  cov.ti = c("X1", "X2"),
  cov.td = "Z_ij",
  method = "ppcm",
  baseline.only = FALSE,
  fixed.window.length = 3,
  int.width = NULL,
  bandwidth = NULL,
  width.subset = FALSE
)

ppcm.res <- as.data.frame(rbind(round(ppcm.fit$est, digits = 3),
                  round(ppcm.fit$se, digits = 3)))
rownames(ppcm.res) <- c("Est.", "S.E.")

ppcm.res %>% knitr::kable(., format = "pipe", padding = 2)
```